Detailed Chemical Abundances with \tc

### 2015-09-08 article/ms.tex
Minor updates

\section{Appendix A: Reproducing this research}
This \article{} has been compiled from the \texttt{git} repository (commit hash \texttt{\gitAbbrevHash} on \texttt{\gitBranch} branch) hosted online at GitHub\footnote{https://www.github.com/andycasey/fireworks}. The complete data analysis, figures and tables included in this \article{} can be reproduced in full using the following commands in a modern Unix-based terminal:
\vspace{0.5em}

>>>>

\section{Appendix A: Reproducing this research}
This \article{} has been compiled from the \texttt{git} repository on \gitAuthorDate{} (commit hash \texttt{\gitAbbrevHash} on \texttt{\gitBranch} branch) hosted online at GitHub\footnote{https://www.github.com/andycasey/fireworks}. The complete data analysis, figures and tables included in this \article{} can be reproduced in full using the following commands in a modern Unix-based terminal:
\vspace{0.5em}
